% ==================================================================================================
% Author: David Oniani
% License: MIT
% ==================================================================================================

\documentclass{article}

\usepackage[dvipsnames]{xcolor}
\usepackage[empty]{fullpage}
\usepackage[english]{babel}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{titlesec}

% Miscellaneous Settings {{{

% Ensure that the generated pdf is machine readable/ATS parsable
\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{fancy}

\fancyhf{}
\fancyfoot{}

\renewcommand{\headrulewidth}{0}
\renewcommand{\footrulewidth}{0}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0}

% Sections formatting
\titleformat{\section}{
    \vspace{-2pt}\scshape\raggedright\large
}{}{0}{}[\color{black}\titlerule\vspace{-4pt}]

% }}}

% Custom Commands {{{

\newcommand{\entry}[4]{
    \vspace{-1pt}
    \item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2\\
        \small#3 & \small #4\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\subentry}[2]{
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & \small #2\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\entriesbegin}{\begin{itemize}[leftmargin=*]}
\newcommand{\entriesend}{\end{itemize}}

\newcommand{\entryitemsstart}{\begin{itemize}[label=\(\circ\)]}
\newcommand{\entryitemsend}{\end{itemize}\vspace{-4pt}}

\newcommand{\entryitem}[1]{\item\small{#1}}
\newcommand{\entrysubitem}[1]{\item[\(\circ\)]\small{#1}\vspace{-4pt}}

\newcommand{\social}[3]{\href{#2}{\faicon{#1} #3}}

% }}}

% Nice-looking URLs {{{

% PDF information and nice-looking urls
\hypersetup{%
    pdfauthor={David Oniani},
    pdftitle={David Oniani's CV},
    pdfsubject={david, oniani, david oniani, cv},
    pdfkeywords={david, oniani, david oniani, cv},
    pdflang={English},
    colorlinks=true,
    linkcolor={black!64!blue},
    citecolor={black!64!blue},
    urlcolor={black!64!blue}
}

% }}}

% ==================================================================================================
% CV Starts Here
% ==================================================================================================

\begin{document}

% Heading {{{

\begin{center}
    \textbf{\href{https://oniani.ai/}{\huge David Oniani}}\\\vspace{16pt}
    \social{mobile}{tel:+16465651224}{+1 (646) 565-1224} \(\circ\)
    \social{globe}{https://oniani.ai/}{oniani.ai} \(\circ\)
    \social{envelope}{mailto:onianidavid@gmail.com}{onianidavid@gmail.com}\vspace{8pt}\\
    \social{github}{https://github.com/oniani}{oniani} \(\circ\)
    \social{linkedin}{https://www.linkedin.com/in/davidoniani/}{davidoniani} \(\circ\)
    \social{youtube-play}{https://www.youtube.com/@davidoniani}{@davidoniani}\vspace{16pt}\\
    Visit \href{https://oniani.ai/}{oniani.ai} for my papers, software, and more!\\\vspace{2pt}
    I also make \href{https://www.youtube.com/@davidoniani}{YouTube videos} about AI and Software Engineering.\\
\end{center}

% }}}

% Education {{{

\section{Education}

\entriesbegin
    \entry{\href{https://www.luther.edu/}{Luther College}}{Decorah, IA}{B.A. Computer Science, Mathematics (magna cum laude)}{Aug. 2017 -- May. 2021}
\entriesend

% }}}

% Technical Skills {{{

\section{Technical Skills}

\entriesbegin
    \entrysubitem{Languages: Python, Go, Modern C++, Shell script, Rust, PostgreSQL, Haskell, Lua, JavaScript, HTML, CSS.}
    \entrysubitem{Tools and Libraries: Linux, Neovim, Git, Docker, PyTorch, Transformers, scikit-learn, matplotlib, numpy, pandas, Flask.}
    \entrysubitem{Theory: Applied Statistics, Deep Learning, Information Theory, Linear Algebra, Multivariable Calculus, Real Analysis, Topology.}
    \entrysubitem{Other Skills: \LaTeX, Markdown, Technical Writing.}
\entriesend

% }}}

% Work experience {{{

\section{Work Experience}

\entriesbegin

\entry{\href{https://www.pitt.edu/}{University of Pittsburgh}}{Pittsburgh, PA}{Machine Learning Research Scientist}{Feb. 2022 -- Present}
\entryitemsstart
    \entryitem{First-authored papers accepted at major NLP and health informatics conferences and journals.}
    \entryitem{Researching Few-Shot Learning (FSL) strategies for accurate and efficient text classification.}
    \entryitem{Lead architect and engineer of \href{https://learn.microsoft.com/en-us/common-data-model/}{CDM}-compliant research data warehouse -- ReDWINE.}
    \entryitem{Giving lectures, presenting my work, and supporting various projects within \href{https://pittnail.github.io/}{PittNAIL} lab.}
\entryitemsend

\entry{\href{https://www.linkedin.com/company/dawnlight/}{DawnLight}}{Palo Alto, CA}{Research Engineer}{Apr. 2021 -- Jan. 2022}
\entryitemsstart
    \entryitem{Developed and maintained AI sensing inference runtime for audio and radar (C++ codebase).}
    \entryitem{Architected and trained highly performant CNN-based ML model for human activity detection.}
    \entryitem{Implemented Python APIs and data engineering pipelines for interacting with data platforms.}
    \entryitem{Together with Principal Scientist, wrote C++ library of signal processing algorithms (libdsp).}
    \entryitem{\href{https://www.linkedin.com/company/dawnlight/}{DawnLight} was \href{https://www.sequoiacap.com}{Sequoia Capital} Backed Ambient Intelligence and Edge Computing Startup.}
\entryitemsend

\entry{\href{https://www.mayoclinic.org/}{Mayo Clinic}}{Rochester, MN}{Artificial Intelligence Researcher}{Feb. 2020 -- Sep. 2020}
\entryitemsstart
    \entryitem{First-authored papers accepted at leading AI and biomedical informatics conferences and journals.}
    \entryitem{Built \href{https://github.com/oniani/covid-19-chatbot}{chatbot} as extension of GPT-2 model by applying BERT, BioBERT, USE, and tf-idf.}
    \entryitem{Utilized \href{https://snap.stanford.edu/node2vec/}{node2vec} for generating COVID-19 network embeddings and built \href{https://oniani.ai/covid-19-network/}{co-occurrence network}.}
    \entryitem{Worked directly under \href{https://www.mayo.edu/research/faculty/shen-feichen-ph-d/bio-20238745}{Dr.~Feichen Shen} and \href{https://www.shrs.pitt.edu/people/yanshan-wang}{Dr.~Yanshan Wang} in division of \href{https://www.mayo.edu/research/faculty/liu-hongfang-ph-d/bio-00055092}{Dr.~Hongfang Liu}.}
\entryitemsend

\entriesend

% }}}

% Select Pulications {{{

\section{Select Publications}

\entriesbegin

\entrysubitem{\footnotesize\href{https://dl.acm.org/doi/abs/10.1145/3388440.3412413}{A Qualitative Evaluation of Language Models on Automatic Question-Answering for COVID-19}\\Proceedings of the 11th ACM International Conference on Bioinformatics, Computational Biology and Health Informatics (ACM-BCB), 2020\\\textbf{First Author}, 25 citations}
\entrysubitem{\footnotesize\href{https://academic.oup.com/jamia/article/27/8/1259/5847598}{Constructing Co-occurrence Network Embeddings to Assist Association Extraction for COVID-19 and Other Coronavirus Infectious Diseases}\\Journal of the American Medical Informatics Association (JAMIA), 2020\\\textbf{First Author}, 18 citations}
\entrysubitem{\footnotesize\href{https://oniani.ai/pdf/machine_translation.pdf}{Toward Improving Health Literacy in Patient Education Materials with Neural Machine Translation Models}\\AMIA Informatics Summit, 2023\\\textbf{First Author}}
\entrysubitem{\footnotesize\href{https://spj.sciencemag.org/journals/hds/aip/9759016/}{Social and Behavioral Determinants of Health in the Era of Artificial Intelligence with Electronic Health Records: A Scoping Review}\\Health Data Science (HDS), 2021\\Co-Author}

\entriesend

% }}}

% Other Experience {{{

\section{Other Experience}

\entriesbegin

% 08/2019 -- 12/2019
\entry{\href{https://www.luther.edu/}{Luther College}}{Decorah, IA}{\href{https://github.com/oniani/ccl-container-types/tree/master/paper}{Research in Programming Languages and Type Theory with Dr.~Alan K. Zaring}}{Fall 2019}
\entryitemsstart
    \entryitem{Introduced notion of container types into CCL programming language.}
    \entryitem{Designed relational operators and type-checking rules for container types.}
\entryitemsend

% 05/2019 -- 07/2019
\subentry{\href{https://github.com/oniani/ira-analysis}{Research in Artificial Intelligence and Authorship Attribution with Professor Richard K. Merritt}}{Summer 2019}
\entryitemsstart
    \entryitem{Trained convolutional neural networks for image recognition using PyTorch.}
    \entryitem{Wrote Python programs for PDF data extraction, data cleanup, and statistical analysis.}
\entryitemsend

% 05/2018 -- 06/2018
\subentry{\href{https://www.luther.edu/news/david-oniani-summer-research}{Research in Unit Testing with Dr.~Roman Yasinovskyy}}{Summer 2018}
\entryitemsstart
    \entryitem{Automated feedback generation for C++ programming course.}
    \entryitem{Redesigned and significantly improved SQL and relational algebra solution checker.}
\entryitemsend

\entriesend

% }}}

% Optional {{{

% Honors and Awards {{{

\section{Honors and Awards}

\entriesbegin

\entrysubitem{Multiple Competitive Scholarships, \href{www.luther.edu}{Luther College} (2017 -- 2020)}
\entrysubitem{Recipient of 2 Luther College Dean's Office Summer Research Awards, \href{www.luther.edu}{Luther College} (2018, 2019)}
\entrysubitem{Dean's List Recipient, \href{www.luther.edu}{Luther College} (All Semesters)}
\entrysubitem{Selected Startup (\href{https://www.linkedin.com/company/unleashar/}{UnleashAR}), TOP 200, \href{http://www.wolvessummit.com/}{Wolves Summit}, Largest Startup Conference in EU (2017).}
\entrysubitem{Gold Medal for Academic Excellence, \href{http://mes.gov.ge/?lang=eng}{Ministry of Education and Science of Georgia} (2016)}
\entrysubitem{Multiple-time Finalist, \href{https://naec.ge/}{National Mathematics Olympiad of Georgia} (2011 -- 2016)}
\entrysubitem{7\textsuperscript{th} Place (TOP 10) \href{https://naec.ge/}{National Mathematics Olympiad of Georgia} (2014)}
\entrysubitem{IMO \& IPhO Nominee, \href{http://mes.gov.ge/?lang=eng}{Ministry of Education and Science of Georgia}, (2014)}

\entriesend

% }}}

% Natural Language Proficiency {{{

\section{Natural Language Proficiency}

\entriesbegin
\entrysubitem{English, Native}
\entrysubitem{Georgian, Native}
\entrysubitem{Russian, Native}
\entrysubitem{Mingrelian, Native}
\entrysubitem{Japanese, Elementary}
\entriesend

% }}}

% Activities and Memberships {{{

\section{Activities and Memberships}

\entriesbegin
\entrysubitem{Member, Pi Mu Epsilon (Math Honor Society), 2020 -- Present}
\entrysubitem{Member, Association for Computing Machinery (ACM), 2022 -- Present}
\entriesend

% }}}

% Volunteer Experience {{{

\section{Volunteer Experience}

\entriesbegin
\entrysubitem{Transparency International Georgia, Georgian Parliamentary Elections' Observation Mission, 2016}
\entriesend

% }}}

% Other Work Experience {{{

\clearpage

\section{Other Work Experience}

\entry{\href{https://www.luther.edu/}{Luther College -- Department of Computer Science}}{Decorah, IA}{Teaching Assistant}{Aug. 2018 -- Jan. 2021}
\entryitemsstart
    \entryitem{\href{https://www.luther.edu/catalog/curriculum/computer-science/}{Computational Models (CS 260) with Dr. Alan K. Zaring} (Fall 2020).}
    \entryitem{\href{https://www.luther.edu/catalog/curriculum/computer-science/}{Object-Oriented Programming With Java (CS 252) with Dr. Shafqat A. Shad} (Fall 2019).}
    \entryitem{\href{https://www.luther.edu/catalog/curriculum/computer-science/}{Introduction to Computer Science (CS 150) with Dr. Alan K. Zaring} (Fall 2018).}
    \entryitem{Held help hours and assisted students with homework assignments.}
    \entryitem{Attended all classes and answered questions during labs.}
\entryitemsend

\entry{\href{https://www.luther.edu/its/}{Luther College -- ITS Workstation}}{Decorah, IA}{ITS Workstation Support Engineer}{Jul. 2019 -- Aug. 2019}
\entryitemsstart
    \entryitem{Was responsible for installing and updating operating systems across campus.}
    \entryitem{Troubleshot technical issues of computer systems.}
    \entryitem{Set up new hardware to be used by college students.}
    \entryitem{Installed software to be used by faculty for teaching purposes.}
\entryitemsend

\entry{\href{https://www.luther.edu/its/}{Luther College, ITS -- Software Development}}{Decorah, IA}{Web Programmer}{Jun. 2018 -- Dec. 2018}
\entryitemsstart
    \entryitem{Contributed to brand new \href{https://norsehub.luther.edu/}{Norse Hub} web system which has successfully replaced \href{https://my.luther.edu/}{my.luther.edu}.}
    \entryitem{Communicated with team, wrote reports, and attended weekly SCRUM meetings.}
    \entryitem{Conducted performance and load testing using JMeter and presented results.}
    \entryitem{Created data visualization tool utilizing JavaScript DOM.}
    \entryitem{Migrated from Microsoft to Linux server and refactored Python code.}
\entryitemsend

\entry{\href{https://www.insta.ge}{Insta LLC}}{Tbilisi, Georgia}{Sales Representative and Marketing Coordinator}{Oct. 2016 -- Jun. 2017}
\entryitemsstart
    \entryitem{Partook in complete rebuild and redesign of sales and marketing departments.}
    \entryitem{Contributed to CRM, was responsible for data gathering, filtering, and entry.}
    \entryitem{Managed social media, was responsible for copywriting and image-editing.}
    \entryitem{Cold-called and contacted clients to build and maintain long-term relationships.}
\entryitemsend

% }}}

% }}}

% ==================================================================================================
% CV Ends Here
% ==================================================================================================

\end{document}
